Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-03-08 papers/05 arxiv v3/journal_v17.tex
final docs

% The paper headers
%\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
%{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

@@

\begin{abstract}
In future distribution grids, prosumers (i.e., energy consumers with storage and/or production capabilities) will trade energy with each other and with the main grid.
%
To ensure an efficient and safe operation of energy trading, in this paper, we formulate a peer-to-peer energy market of prosumers as a generalized aggregative game, in which a network operator is responsible to enforce the operational constraints of the system.
%
We design a distributed market-clearing mechanism with convergence guarantee to an economically-efficient, strategically-stable, and operationally-safe configuration (i.e., a variational generalized Nash equilibrium). 
%
Numerical studies on the IEEE 37-bus testcase show the scalability of the proposed approach and suggest that active participation in the market is beneficial for both prosumers and the network operator.  
\end{abstract}
\vspace{-5pt}
\begin{IEEEkeywords}
	Prosumers, energy management, distributed algorithm, generalized Nash equilibrium
\end{IEEEkeywords}
%====================================================
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}
\section*{Nomenclature}
\begin{table}[h]
	\small 
	\begin{tabular}{l c l}
		\toprule
		\multicolumn{3}{c}{Variables and Cost Functions} \\
		\hline
		$f^{\mathrm{di}}$ & [\euro] & cost of the \underline{di}spatchable units  \\
		%$f^{\ell}$ & & real power line between two neighboring busses  \\
		$f^{\mathrm{mg}}$ & [\euro] & cost of trading with the \underline{m}ain \underline{g}rid  \\
		$f^{\mathrm{st}}$ & [\euro] & cost  of the \underline{st}orage units  \\
		$f^{\mathrm{tr}}$ & [\euro]& cost  of \underline{tr}ading with other prosumers  \\
		$J$ &[\euro]  & total cost function of each prosumer \\
		$\lambda^{\mathrm{mg}}$ &[\euro/kWh] & dual variable for grid trading constraints %\eqref{eq:p_mg_bound}
		\\
		$\mu^{\mathrm{pb}}$ & [\euro/kWh]& dual variable for power balance constraints \\
		$\mu^{\mathrm{tg}}$ &[\euro/kWh] & dual variable for grid physical constraints
		%	 \eqref{eq:grid_const2}
		\\
		$\mu^{\mathrm{tr}}$ &[\euro/kWh] & dual variable for reciprocity constraints \\
		$p^{\mathrm{di}}$ & [kW]& power generated by {di}spatchable units  \\
		$p^{\ell}$ &[kW] & real power line of two neighboring busses  \\
		$p^{\mathrm{mg}}$ &[kW] & power traded with the {m}ain {g}rid  \\
		{$p^{\mathrm{ch}}$} &[kW] & {charging power of the {st}orage units}  \\
		{$p^{\mathrm{ds}}$} &[kW] & {discharging power of the {st}orage units}  \\
		$p^{\mathrm{tg}}$ &[kW] & power exchanged between bus and main grid \\	
		$p^{\mathrm{tr}}$ & [kW]& power {tr}aded with another prosumer  \\
		$q^{\ell}$ &[kVAr] & reactive power line   \\
		$\sigma^{\mathrm{mg}}$ &[kW] & aggregate of active load on the main grid \\
		$v$ &p.u. & voltage magnitude \\
		$x$ & [$\%$] & state of charge of the storage units\\
		$\theta$ & [rad]& voltage angle \\
		\hline

	\end{tabular}
\end{table} 
\smallskip
\begin{table}[!h]
	\small 
	\begin{tabular}{l c l}
				\toprule
		\multicolumn{3}{c}{Parameters} \\
		\hline
		$\alpha, \beta, \gamma$ &- & step sizes of the proposed algorithm \\
		$b$ & [kW]& aggregate of passive consumer demand \\
		$B$ &[ohm$^{-1}$] & line susceptance \\
		$ c^{\mathrm{di}}$ &[\euro/kWh] & linear coefficient (coeff.) on the cost \\ & & of dispatchable units (DU) \\
		$c^{\mathrm{ta}}$ & [\euro/kWh]& trading tariff \\
		$c^{\mathrm{tr}}$ &[\euro/kWh] & per-unit cost of trading \\
		$d^{\mathrm{mg}}$ & [\euro/kWh$^2$]& coeff. on the cost of trading with \\
		& & the main grid \\
		$e^{\mathrm{cap}}$ &[kWh] & max. capacity of the storage units \\
		{$\eta^{\mathrm{st}}$} & - & {leakage coefficient of storage units}\\
		{$ \eta^{\mathrm{ch}}$}, {$ \eta^{\mathrm{ds}}$} & - & {charging and discharging efficiencies}\\
%		 & - & {discharging efficiency}\\
		$G$ & [ohm$^{-1}$]  & line conductance \\
		$H$ &- & time horizon \\
		$\bar p^{\mathrm{ch}}$ &[kW]  & max. \underline{ch}arging power of the storages \\
		$p^{\mathrm{d}}$ &[kW]  & power \underline{d}emand 
		%(the difference between  \\
		%\> load and non-dispatchable generation) 
		\\
		{$\bar p^{\mathrm{ds}}$} &[kW] & max. \underline{d}i\underline{s}c{h}arging power of the storages \\
		$\overline{p}^{\mathrm{di}}, \underline{p}^{\mathrm{di}}$ &[kW]  & max. and min. power generated by DU\\
		$\overline{p}^{\mathrm{mg}}, \underline{p}^{\mathrm{mg}}$ &[kW]  & max. and min. total power  \\ & & traded with the main grid\\
		%$p^{\mathrm{pd}}$ & & passive power demand  \\
		$\overline{p}^{\mathrm{tr}}$ &[kW]  & max. power traded between prosumers \\
		$Q^{\mathrm{di}}$ &[\euro/kWh$^2$] & quadratic coeff. on the cost of DU \\
		$Q^{\mathrm{st}}$ & [\euro/kWh$^2$]& coeff. on the cost of storage units \\
		$\overline{s}$ & [kVA] & max. line capacity \\
		$T_s$ & [hour] & sampling time \\
		$\overline{v}, \underline{v}$ & p.u. & max. and min. voltage magnitude \\
		$\overline{x},\underline{x}$ &p.u. & max. and min. state of charge \\
		$\overline{\theta}, \underline{\theta}$ & [rad] & max. and min. voltage angle \\
		\hline
		\toprule
		\multicolumn{3}{c}{Sets}  \\
		\hline 
		$\mc B$ & & set of busses in the electrical network \\
		$\mc B^{\mathrm{mg}}$ & & set of busses connected to main grid\\
		$\mathcal{C}$ & & coupling constraint set \\
		$\mc E$ & & set of links in the trading network\\
		$\mathcal{G}^{\mathrm{t}}$ & & graph representing trading network \\
		$\mathcal{G}^{\mathrm{p}}$ & & graph representing physical network \\
		$\mc H$ & & set of discrete-time indices \\
		$\mc L$ & & set of power lines (links)\\
		$\mathcal{N}$ & & set of prosumers \\
		$\mathcal{N}^+$ & & set of prosumers and network operator\\
		$\mathcal{N}_i$ & & set of trading partners of prosumer $i$ \\
		$\mathcal{N}_y^{\mathrm{b}}$ & & set of prosumers of bus $y$ \\
		$\mc P$ & & set of passive consumers \\
		$\mc P_y^{\mathrm{b}}$& &set of passive consumers of bus $y$ \\
		$\mathcal{U}$ & & local constraint set \\ 
		\bottomrule

@@

%
{
The main advantage of our decentralized market design is that its equilibria are not only economically-optimal but also strategically-stable (i.e., no prosumer has any incentive to unilaterally deviate), operationally-safe and reliable (i.e., the network operational requirements are met), and socially-fair (i.e., the marginal loss for satisfying the grid constraints is the same for each prosumer). 
%
%
Furthermore, we design a provably-convergent, scalable and distributed market-clearing algorithm based on the proximal-point method for monotone inclusion problems	\cite[\S~23]{bauschke2011convex} (Section \ref{sub:alg}). 
%\red{discuss differences from \cite{belgioioso2020energy}}.
Finally, we investigate via extensive numerical studies: (i)  the effectiveness of the proposed market framework; (ii) the impact of distributed generation, storage and P2P tradings in distribution grids; and (iii) the scalability of the proposed market-clearing mechanism with respect to both the number of prosumers and the number of P2P tradings in the distribution network (Section \ref{sub:case_std}).
}

\smallskip
\subsubsection*{Notation}
$\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$).
%;
%to improve clarity, we may add the dimension of these matrices/vectors as subscript.
$A \otimes B$ denotes the Kronecker product between the matrices $A$ and $B$. For a square matrix $A \in \R^{n \times n}$, its transpose is $A^\top$, $[A]_{i,j}$ represents the element on the row $i$ and column $j$. $A \succ 0$ ($\succcurlyeq 0$) stands for positive definite (semidefinite) matrix.
%Given $N$ vectors $x_1 \in \bb R^{n_1}, x_2 \in \bb R^{n_2},\ldots, x_N \in \R^{n_N}$, $x := \col\left(x_1,\ldots,x_N\right) = [ x_1^\top, \ldots , x_N^\top ]^\top$.
{For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square symmetric matrix $A \succ 0$}. 
%\smallskip
%\subsubsection*{Operator theoretic definitions}
%Here, $\Id(\cdot)$ denotes the identity operator. The mapping $\iota_{S}:\R^n \rightarrow \{ 0, \, \infty \}$ denotes the indicator function for the set $\mc{S} \subseteq \R^n$, i.e., $\iota_{S}(x) = 0$ if $x \in S$, $\infty$ otherwise. 
For a closed set $S \subseteq \R^n$, the mapping $\proj_{S}:\R^n \rightarrow S$ denotes the projection onto $S$, i.e., $\proj_{S}(x) = \argmin_{y \in S} \left\| y - x\right\|$. 
%The set-valued mapping $\nc_{S}: \R^n \rightrightarrows \R^n$ denotes the normal cone operator for the the set $S \subseteq \R^n$, i.e., $\nc_{S}(x) = \varnothing$ if $x \notin S$, $\left\{ v \in \R^n \mid \sup_{z \in S} \, v^\top (z-x) \leq 0  \right\}$ otherwise. 
%A set-valued mapping $\mathcal{F} : \R^n \rightrightarrows \R^n$ is (strictly) monotone if $(u-v)^\top  (x-y) \geq (>) \, 0$ for all $x \neq y \in \R^n$, $u \in \mathcal{F} (x)$, $v \in \mathcal{F} (y)$.
% $\fix\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid x \in \mathcal{F}(x) \right\}$ and $\zer\left( \mathcal{F}\right) := \left\{ x \in \R^n \mid 0 \in \mathcal{A}(x) \right\}$ denote the set of fixed points and of zeros, respectively.

%\subsection{Generalized Nash equilibrium problems}
%\paragraph*{Description of a GNEPs} Key concepts: non-cooperative agents, utility function, coupling constraints.

@@

\begin{figure}
	\centering
	%\includegraphics[scale=1.4]{figures/37bus_ex}
	\includegraphics[width=0.95\columnwidth]%
%{figures/NF/37bus_sysIPE1}%
{figures/37bus_sys_f1}
\smallskip
	\caption{Left plot: A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles); busses are represented by black circles, physical lines in $\mc L$ by solid lines. Right plot: P2P trading network, where trading relations ($\mc E$) are represented by blue double-arrow lines.
	}
	\label{fig:GGp}
\end{figure} 
%\begin{figure}
%	\centering
%	\includegraphics[scale=1.4]{figures/37bus_ex}
%	\caption{A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles). Busses are represented by black circles, physical lines in $\mc L$ by solid lines, whereas trading relations ($\mc E$) by dash-dotted blue lines.
%	}
%	\label{fig:GGp}
%\end{figure}

@@

Each agent $i$ is self-interested and wants to compute an optimal decision, $u_i^*$, that solves its local optimization problem%
\begin{subequations}
	\label{eq:locOpt}
	\begin{empheq}[left=u_i^*\in \empheqlbrace]{align}
	\label{eq:cost_gen}	
	& 
	\arg\min_{{u}_i }  \;   J_{i}\left(
	u_{i} , u_{-i} 	
	\right) \\[.2em]
	\label{eq:const_gen}
	&\quad \text{s.t. } \; \quad {u}_{i} \in  \mc U_i\\
	&\qquad \quad \; \; (u_i, {u}_{-i}) \in \mc C,% \\
	%
%	& \qquad \qquad
%	u_{i} \in \mc C_i(u_{-i})	
	\end{empheq}
\end{subequations} 
where $J_i$ is the cost function of agent $i$, $\mc U_i$ is the local constraint set, and $\mc C$ is the set of coupling constraints. 
%\smallskip
In the remainder of this section, we describe $J_i$, $\mc U_i$, and $\mc C$, upon which we postulate standard assumptions, as formalized next.
%We build the model upon \cite[\S~II]{belgioioso2020energy} and discuss our extension.

@@

%\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$ and defined as in \cite{hans2018} as follows:
\begin{equation}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. {The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}},
%
\begin{equation}
	\begin{aligned}
	%	\left.
	%	\begin{array}{c}
			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\tfrac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\tfrac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %\forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\[.2em]
		\\
			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
	%	\end{array}
	%	\hspace{-5pt} \right\} & \begin{matrix}
	%	\end{matrix} 
	\\
		p_{i}^{\mathrm{ch}} &= 0, \ \ p_{i}^{\mathrm{ds}}= 0,\qquad \qquad \quad \  \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$%
%\footnote{In \cite{atzeni2013}, the charging and discharging power are defined separately, which is actually a better representation. However, the optimal strategies that they produce satisfies the constraint that charging and discharging must be mutually exclusive (see footnote 1 in \cite{atzeni2013}). From other papers, they usually have boolean variables to ensure this constraint and we want to avoid that.}
, {$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  %$b_i~=~-\frac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}$, with 
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas ${\overline p^{\mathrm{ch}}_i} \geq 0$ and ${\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.

@@

%Clearly, each pair of neighboring agent $i$ and $j$ has the same reciprocity constraint.

%\smallskip
\paragraph*{Power traded with the main grid} Let $p_{i,h}^{\mathrm{mg}}$ be the power prosumer $i$ imports from the main grid at time $h \in \mc H$. As in \cite{atzeni2013}, we assume that the electricity unit price at each time step $h \in \mc H	$ depends on the total consumption,
\begin{equation}
c_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h)= d_h^{\mathrm{mg}}\cdot {\left(\sigma^{\textrm{mg}}_h + b_h \right)}^2,
\end{equation}
where $d_h^{\mathrm{mg}}$ is a positive price parameter, whereas $\sigma^{\textrm{mg}}_h$ and $b_h$ denote the \textit{aggregate active} and \textit{passive} \textit{load on the grid}, i.e., 
\begin{equation} \label{eq:Aggr}
\sigma^{\textrm{mg}}_h = \sum_{i\in\mathcal{N}} p_{i,h}^{\mathrm{mg}},
\quad
b_h =\sum_{i\in \mathcal P}p_{i,h}^{\mathrm{d}},
 \quad \forall h \in \mathcal H.
\end{equation} 
Therefore, the total cost incurred by prosumer $i$, over the horizon $\mc H$, for trading with the main grid is given by
%objective function of agent $i$ associated to the trading with the main grid, denoted by $f_{i}^{\mathrm{mg}}$, is defined as 
\begin{equation}
\begin{aligned} \textstyle
f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right) &= \sum_{h\in \mc H}c_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h) \, \frac{p_{i,h}^{\mathrm{mg}}}{\sigma_h^{\textrm{mg}} + b_h}\\
%&= \sum_{h\in \mc H}d_h^{\mathrm{mg}}\left(\sum_{j\in\mathcal{N}}p_{j,h}^{\mathrm{mg}}\right)p_{i,h}^{\mathrm{mg}}, 
&= \sum_{h\in \mc H}  d_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h+b_h) \, p_{i,h}^{\mathrm{mg}},
\label{eq:f_mg}
\end{aligned}
\end{equation}
%where $p_{i}^{\mathrm{mg}} = \col((p_{i,h}^{\mathrm{mg}})_{h\in\mc H})$ and $b =\col((b_h)_{h\in\mc H})$.
We note that the cost function \eqref{eq:f_mg} assumes equal electricity price at each distribution node and the consideration of power losses and congestion, which may result in different price at different node, is left for future work.

>>>>

@@

\begin{abstract}
In future distribution grids, prosumers (i.e., energy consumers with storage and/or production capabilities) will trade energy with each other and with the main grid.
%
To ensure an efficient and safe operation of energy trading, in this paper, we formulate a peer-to-peer energy market of prosumers as a generalized aggregative game, in which a network operator is responsible to enforce the operational constraints of the system.
%
We design a distributed market-clearing mechanism with convergence guarantee to an economically-efficient, strategically-stable, and operationally-safe configuration (i.e., a variational generalized Nash equilibrium). 
%
Numerical studies on the IEEE 37-bus testcase show the scalability of the proposed approach and suggest that active participation in the market is beneficial for both prosumers and the network operator.  
\end{abstract}
\vspace{-5pt}
\begin{IEEEkeywords}
	Prosumers, energy management, distributed algorithm, generalized Nash equilibrium
\end{IEEEkeywords}
%====================================================
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-10pt}
\section*{Nomenclature}
\begin{table}[h]
	\small 
	\begin{tabular}{l c l}
		\toprule
		\multicolumn{3}{c}{Variables and Cost Functions} \\
		\hline
		$f^{\mathrm{di}}$ & [\euro] & cost of the \underline{di}spatchable units  \\
		$f^{\mathrm{mg}}$ & [\euro] & cost of trading with the \underline{m}ain \underline{g}rid  \\
		$f^{\mathrm{st}}$ & [\euro] & cost  of the \underline{st}orage units  \\
		$f^{\mathrm{tr}}$ & [\euro]& cost  of \underline{tr}ading with other prosumers  \\
		$J$ &[\euro]  & total cost function of each prosumer \\
		$\lambda^{\mathrm{mg}}$ &[\euro/kWh] & dual variable for grid trading constraints 		\\
		$\mu^{\mathrm{pb}}$ & [\euro/kWh]& dual variable for power balance constraints \\
		$\mu^{\mathrm{tg}}$ &[\euro/kWh] & dual variable for grid physical constraints
		\\
		$\mu^{\mathrm{tr}}$ &[\euro/kWh] & dual variable for reciprocity constraints \\
		$p^{\mathrm{di}}$ & [kW]& power generated by {di}spatchable units  \\
		$p^{\ell}$ &[kW] & real power line of two neighboring busses  \\
		$p^{\mathrm{mg}}$ &[kW] & power traded with the {m}ain {g}rid  \\
		{$p^{\mathrm{ch}}$} &[kW] & {charging power of the {st}orage units}  \\
		{$p^{\mathrm{ds}}$} &[kW] & {discharging power of the {st}orage units}  \\
		$p^{\mathrm{tg}}$ &[kW] & power exchanged between bus and main grid \\	
		$p^{\mathrm{tr}}$ & [kW]& power {tr}aded with another prosumer  \\
		$q^{\ell}$ &[kVAr] & reactive power line   \\
		$\sigma^{\mathrm{mg}}$ &[kW] & aggregate of active load on the main grid \\
		$v$ &p.u. & voltage magnitude \\
		$x$ & [$\%$] & state of charge of the storage units\\
		$\theta$ & [rad]& voltage angle \\
		\hline

	\end{tabular}
\end{table} 
\smallskip
\begin{table}[!h]
	\small 
	\begin{tabular}{l c l}
				\toprule
		\multicolumn{3}{c}{Parameters} \\
		\hline
		$\alpha, \beta, \gamma$ &- & step sizes of the proposed algorithm \\
		$b$ & [kW]& aggregate of passive consumer demand \\
		$B$ &[ohm$^{-1}$] & line susceptance \\
		$ c^{\mathrm{di}}$ &[\euro/kWh] & linear coefficient (coeff.) on the cost \\ & & of dispatchable units (DU) \\
		$c^{\mathrm{ta}}$ & [\euro/kWh]& trading tariff \\
		$c^{\mathrm{tr}}$ &[\euro/kWh] & per-unit cost of trading \\
		$d^{\mathrm{mg}}$ & [\euro/kWh$^2$]& coeff. on the cost of trading with \\
		& & the main grid \\
		$e^{\mathrm{cap}}$ &[kWh] & max. capacity of the storage units \\
		{$\eta^{\mathrm{st}}$} & - & {leakage coefficient of storage units}\\
		{$ \eta^{\mathrm{ch}}$}, {$ \eta^{\mathrm{ds}}$} & - & {charging and discharging efficiencies}\\
		$G$ & [ohm$^{-1}$]  & line conductance \\
		$H$ &- & time horizon \\
		$\bar p^{\mathrm{ch}}$ &[kW]  & max. \underline{ch}arging power of the storages \\
		$p^{\mathrm{d}}$ &[kW]  & power \underline{d}emand 
		\\
		{$\bar p^{\mathrm{ds}}$} &[kW] & max. \underline{d}i\underline{s}c{h}arging power of the storages \\
		$\overline{p}^{\mathrm{di}}, \underline{p}^{\mathrm{di}}$ &[kW]  & max. and min. power generated by DU\\
		$\overline{p}^{\mathrm{mg}}, \underline{p}^{\mathrm{mg}}$ &[kW]  & max. and min. total power  \\ & & traded with the main grid\\
		%$p^{\mathrm{pd}}$ & & passive power demand  \\
		$\overline{p}^{\mathrm{tr}}$ &[kW]  & max. power traded between prosumers \\
		$Q^{\mathrm{di}}$ &[\euro/kWh$^2$] & quadratic coeff. on the cost of DU \\
		$Q^{\mathrm{st}}$ & [\euro/kWh$^2$]& coeff. on the cost of storage units \\
		$\overline{s}$ & [kVA] & max. line capacity \\
		$T_s$ & [hour] & sampling time \\
		$\overline{v}, \underline{v}$ & p.u. & max. and min. voltage magnitude \\
		$\overline{x},\underline{x}$ &p.u. & max. and min. state of charge \\
		$\overline{\theta}, \underline{\theta}$ & [rad] & max. and min. voltage angle \\
		\hline
		\toprule
		\multicolumn{3}{c}{Sets}  \\
		\hline 
		$\mc B$ & & set of busses in the electrical network \\
		$\mc B^{\mathrm{mg}}$ & & set of busses connected to main grid\\
		$\mathcal{C}$ & & coupling constraint set \\
		$\mc E$ & & set of links in the trading network\\
		$\mathcal{G}^{\mathrm{t}}$ & & graph representing trading network \\
		$\mathcal{G}^{\mathrm{p}}$ & & graph representing physical network \\
		$\mc H$ & & set of discrete-time indices \\
		$\mc L$ & & set of power lines (links)\\
		$\mathcal{N}$ & & set of prosumers \\
		$\mathcal{N}^+$ & & set of prosumers and network operator\\
		$\mathcal{N}_i$ & & set of trading partners of prosumer $i$ \\
		$\mathcal{N}_y^{\mathrm{b}}$ & & set of prosumers of bus $y$ \\
		$\mc P$ & & set of passive consumers \\
		$\mc P_y^{\mathrm{b}}$& &set of passive consumers of bus $y$ \\
		$\mathcal{U}$ & & local constraint set \\ 
		\bottomrule

@@

%
{
The main advantage of our decentralized market design is that its equilibria are not only economically-optimal but also strategically-stable (i.e., no prosumer has any incentive to unilaterally deviate), operationally-safe and reliable (i.e., the network operational requirements are met), and socially-fair (i.e., the marginal loss for satisfying the grid constraints is the same for each prosumer). 
%
%
Furthermore, we design a provably-convergent, scalable and distributed market-clearing algorithm based on the proximal-point method for monotone inclusion problems	\cite[\S~23]{bauschke2011convex} (Section \ref{sub:alg}). 
Finally, we investigate via extensive numerical studies: (i)  the effectiveness of the proposed market framework; (ii) the impact of distributed generation, storage and P2P tradings in distribution grids; and (iii) the scalability of the proposed market-clearing mechanism with respect to both the number of prosumers and the number of P2P tradings in the distribution network (Section \ref{sub:case_std}).
}

\smallskip
\subsubsection*{Notation}
$\R$ denotes the set of real numbers, $\bb N$ denotes the set of natural numbers, and  $\bs{0}$ ($\bs{1}$) denotes a matrix/vector with all elements equal to $0$ ($1$). 
$A \otimes B$ denotes the Kronecker product between the matrices $A$ and $B$. For a square matrix $A \in \R^{n \times n}$, its transpose is $A^\top$, $[A]_{i,j}$ represents the element on the row $i$ and column $j$. $A \succ 0$ ($\succcurlyeq 0$) stands for positive definite (semidefinite) matrix. 
{For any $x \in \bb R^n$, $\|x\|_A^2 = x^\top A x,$ with square symmetric matrix $A \succ 0$}. 
For a closed set $S \subseteq \R^n$, the mapping $\proj_{S}:\R^n \rightarrow S$ denotes the projection onto $S$, i.e., $\proj_{S}(x) = \argmin_{y \in S} \left\| y - x\right\|$.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.95\columnwidth]{figures/37bus_sys_f1.eps}
\smallskip
	\caption{Left plot: A modified IEEE 37-bus network with 12 prosumers (boxes) and 15 passive loads (black triangles); busses are represented by black circles, physical lines in $\mc L$ by solid lines. Right plot: P2P trading network, where trading relations ($\mc E$) are represented by blue double-arrow lines.
	}
	\label{fig:GGp}
\end{figure}

@@

Each agent $i$ is self-interested and wants to compute an optimal decision, $u_i^*$, that solves its local optimization problem%
\begin{subequations}
	\label{eq:locOpt}
	\begin{empheq}[left=u_i^*\in \empheqlbrace]{align}
	\label{eq:cost_gen}	
	& 
	\arg\min_{{u}_i }  \;   J_{i}\left(
	u_{i} , u_{-i} 	
	\right) \\[.2em]
	\label{eq:const_gen}
	&\quad \text{s.t. } \; \quad {u}_{i} \in  \mc U_i\\
	&\qquad \quad \; \; (u_i, {u}_{-i}) \in \mc C,
	\end{empheq}
\end{subequations} 
where $J_i$ is the cost function of agent $i$, $\mc U_i$ is the local constraint set, and $\mc C$ is the set of coupling constraints. 
%\smallskip
In the remainder of this section, we describe $J_i$, $\mc U_i$, and $\mc C$, upon which we postulate standard assumptions, as formalized next.

@@

%\smallskip
\paragraph*{Storage units} 
Each prosumer might also minimize the usage of its storage units, for instance, in order to reduce its degradation. The corresponding cost function is denoted by $f_{i}^{\mathrm{st}}:\mathbb{R}^{H} \to \mathbb{R}$ and defined as in \cite{hans2018} as follows:
\begin{equation}
f_{i}^{\mathrm{st}}(p_{i}^{\mathrm{ch}}, p_{i}^{\mathrm{ds}})= \|p_{i}^{\mathrm{ch}}\|_{Q_i^{\mathrm{st}}}^2 + \|p_{i}^{\mathrm{ds}}\|_{Q_i^{\mathrm{st}}}^2, \label{eq:f_st}
\end{equation}
where $Q_i^{\mathrm{st}}\succcurlyeq0$. {The battery charging and discharging profiles, $p_{i}^{\mathrm{ch}} = \col((p_{i,h}^{\mathrm{ch}})_{h\in \mc H})$ and $p_{i}^{\mathrm{ds}} = \col((p_{i,h}^{\mathrm{ds}})_{h\in \mc H})$, respectively, are constrained by the battery dynamics \cite{atzeni2013,zhong2019online}},
%
\begin{equation}
	\begin{aligned}
			x_{i,h+1} &=\eta_i^{\mathrm{st}} x_{i,h} +\tfrac{T_{\mathrm{s}}}{e^{\mathrm{cap}}_{i}}(\eta_i^{\mathrm{ch}} p_{i,h}^{\mathrm{ch}} -(\tfrac{1}{\eta_i^{\mathrm{ds}}})p_{i,h}^{\mathrm{ds}}), %		\\
			\underline{x}_i &\leq x_{i,h+1} \leq \overline{x}_i,  \qquad \forall i \in \mc N^{\mathrm{st}}, \forall h \in \mc H,\\%[.2em]
			{p}_{i}^{\mathrm{ch}} &\in [0,\overline{{p}}_{i}^{\mathrm{ch}}], \ \ {p}_{i}^{\mathrm{ds}} \in [0,\overline{{p}}_{i}^{\mathrm{ds}}],  \quad  \forall i \in \mc N^{\mathrm{st}},
	\\
		p_{i}^{\mathrm{ch}} &= 0, \ \ p_{i}^{\mathrm{ds}}= 0,\qquad \qquad \quad \  \forall i \notin \mc N^{\mathrm{st}},
	\end{aligned}
	\label{eq:x}
\end{equation}
where $x_{i,h} $ denotes the state of charge (SoC) of the storage unit at time $h \in \mc H$, 
{$\eta_i^{\mathrm{st}}, \eta_i^{\mathrm{ch}}, \eta_i^{\mathrm{ds}} \in (0,1]$ denote  the leakage coefficient of the storage, charging, and discharging efficiencies, respectively, while }  
$T_{\mathrm{s}}$ and $e^{\mathrm{cap}}_{i}$ denote sampling time and maximum capacity of the storage, respectively. Moreover, $\underline{x}_i,\overline{x}_i  \in [0,1]$  denote the minimum and the maximum SoC of the storage unit of prosumer $i$, respectively, whereas ${\overline p^{\mathrm{ch}}_i} \geq 0$ and ${\overline p^{\mathrm{ds}}_i} \geq 0$ denote the maximum charging and discharging power of the storage unit. Finally, we denote by  $\mathcal{N}^{\mathrm{st}}\subseteq\mathcal{N}$ 	the set of prosumers that own a storage unit.

@@

%\smallskip
\paragraph*{Power traded with the main grid} Let $p_{i,h}^{\mathrm{mg}}$ be the power prosumer $i$ imports from the main grid at time $h \in \mc H$. As in \cite{atzeni2013}, we assume that the electricity unit price at each time step $h \in \mc H	$ depends on the total consumption,
\begin{equation}
c_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h)= d_h^{\mathrm{mg}}\cdot {\left(\sigma^{\textrm{mg}}_h + b_h \right)}^2,
\end{equation}
where $d_h^{\mathrm{mg}}$ is a positive price parameter, whereas $\sigma^{\textrm{mg}}_h$ and $b_h$ denote the \textit{aggregate active} and \textit{passive} \textit{load on the grid}, i.e., 
\begin{equation} \label{eq:Aggr}
\sigma^{\textrm{mg}}_h = \sum_{i\in\mathcal{N}} p_{i,h}^{\mathrm{mg}},
\quad
b_h =\sum_{i\in \mathcal P}p_{i,h}^{\mathrm{d}},
 \quad \forall h \in \mathcal H.
\end{equation} 
Therefore, the total cost incurred by prosumer $i$, over the horizon $\mc H$, for trading with the main grid is given by
\begin{equation}
\begin{aligned} \textstyle
f_{i}^{\mathrm{mg}}\left( p_{i}^{\mathrm{mg}},\sigma^{\textrm{mg}} \right) &= \sum_{h\in \mc H}c_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h) \, \frac{p_{i,h}^{\mathrm{mg}}}{\sigma_h^{\textrm{mg}} + b_h}\\
&= \sum_{h\in \mc H}  d_h^{\mathrm{mg}}(\sigma^{\textrm{mg}}_h+b_h) \, p_{i,h}^{\mathrm{mg}},
\label{eq:f_mg}
\end{aligned}
\end{equation}
We note that the cost function \eqref{eq:f_mg} assumes equal electricity price at each distribution node and the consideration of power losses and congestion, which may result in different price at different node, is left for future work.
